\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright

% Section formatting
\titleformat{\section}{
  \vspace{4pt}\scshape\large\raggedright
}{}{0em}{}[\titlerule \vspace{-4pt}]

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{center}
    {\Huge \scshape Jayanth A Gatti} \\ \vspace{2pt}
    \href{mailto:jayanthagatti2003@gmail.com}{jayanthagatti2003@gmail.com} $|$ Phone: +91 9353416619 $|$ $|$ Bengaluru, Karnataka $|$ 
    \href{https://www.linkedin.com/in/jayanth-a-gatti-836988227/}{LinkedIn} $|$ 
    \href{https://github.com/jayanthagatti}{GitHub}
\end{center}

%-----------PROFILE SUMMARY-----------
\section*{Profile Summary}
Motivated and detail-oriented Information Science graduate with strong foundational knowledge in Python Full Stack Development. Proficient in Python, Django, MySQL, and front-end technologies. Passionate about learning new Technologies and Eager to contribute to real-world projects and grow in a collaborative, tech-driven environment. 

%-----------EDUCATION-----------
\section{Education}
\textbf{Bachelor of Engineering in Information Science} \hfill Dec 2021 -- Present \\ Jawaharlal Nehru New College of Engineering, Shivamoga \\
Current CGPA: 8.48

\vspace{4pt}
\textbf{PU (Pre-University)}, Pace UM PU College, Shivamogga \hfill 2019 -- 2021 \\
Percentage: 68\%

\vspace{4pt}
\textbf{SSLC}, Kendriya Vidyalaya School,Shivamogga \hfill 2018 -- 2019 \\
Percentage: 73\%

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.5cm, itemsep=1pt]
    \item \textbf{Languages:} Python, JavaScript, HTML, CSS
    \item \textbf{Frameworks/Libraries:} Django, Flask,Numpy , Pandas, Matplotlib, Scikit-Learn
    \item \textbf{Tools \& Platforms} VS Code, Pycharm, MySQL Workbench, Jupyter notebook  
    \item \textbf{Databases:} MySQL
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}

\textbf{Potato Disease Identification Using Deep Learning (Python,Flask,HTML,CSS, Stream-lit,Tensor flow)} \hfill Oct 2024 -- Present \\
\begin{itemize}[leftmargin=0.5cm]
    \item The project aim is to develop a deep learning model using CNN to classify potato leaf images into three categories: Late Blight, Early Blight, and Healthy. The goal is to provide an automated solution for early disease detection, helping reduce crop losses and improve yield.  
\end{itemize}

\textbf{Prediction of Diabetes(Python Flask,HTML,CSS, ML Libraries)} \hfill Mar 2025 --  May 2025 \\
\begin{itemize}[leftmargin=0.5cm]
    \item Built a machine learning-based web app using Python, Flask, and scikit-learn to predict whether patient has diabetes or not based on the report Using Machine Learning Libraries. Designed a user-friendly front end with HTML and CSS.
\end{itemize}

\textbf { palle Admin Project(Python Django,MySQL,HTML,CSS,Bootstrap)} \hfill Apr 2025 --  May 2025 \\
\begin{itemize}[leftmargin=0.5cm]
    \item The Palle Admin project is a Django-based role-based system where Admins can fully manage employees and students, while Sales users have limited access. It uses Django object to relational mapping, Model Forms, and function-based views for secure login, dynamic dashboards, and student assignment through the added by field. 
\end{itemize}

%-----------INTERNSHIP-----------
\section{Internship}

\textbf{Python Full Stack Intern, Palle Technologies, Bangalore} \hfill February 2025 - May 2025 \\
\begin{itemize}[leftmargin=0.5cm]
    \item Gained Practical Knowledge on Python, Django, MySQL and front end technologies.Built a project a full stack which conatains both front and backend technologies and database. 
\end{itemize}



%-----------CERTIFICATIONS-----------
\section{Courses \& Certifications}
\begin{itemize}[leftmargin=0.5cm]
    \item Full Stack Web Development Training – Palle Technologies(2025)
    \item Cyber Security - Edunet Foundation
    \item Deloitte Australia- Data Analytics Job Simulation - Forage
\end{itemize}




\end{document}